\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

The most important limitation rather comes from the coverage period. Information about the port of entry are only available since 1989, which is already smaller than our full sample starting in 1974. On top of that, because of the Covid situation, the US Bureau of Census was only able to send us the data relative to the years 1997-1999 and 2001-2019. Implementing the referee's method would hence necessarily reduce the time coverage of our analysis by more than 20 years (skipping the 1974-1996 years in particular). In our view, the historical coverage is interesting per se, as it provides useful insights about how transport costs have evolved over time. Eliminating this dimension of the paper would be detrimental to its contribution.

\item[Concern 2] The suggested method features less accuracy in the estimation of the $\beta$.

If we take the value of the $\beta$ by itself, there is no clear criteria to discriminate between the value estimated with our method and the one obtained with the suggested method (when, of course, run on the same sample). Further, as shown in Table \ref{tab_comp_referee1_baseline}, no clear sign of a potential upwards or downwards bias that would be attached to our method. Things are more clear-cut in terms of accuracy of the estimation. Specifically, our method yields a more precise estimation of the $\beta$ than the referee's method. To develop on this, for each year and transport mode:
    \begin{itemize}
    \item With the referee's method, we estimate one value for the share of additive component $\beta$ at the $i,s$ level denoted $\hat{\beta}^{ref}_{is(k)}$ associated with a standard deviation $SD_{is}$, by year and transport mode. From this, we can compute the size of the 5-95\% confidence interval $CI^{ref}_{is} = \hat{\beta}_{is}^{max,ref} - \hat{\beta}_{is}^{min,ref}$ where:
        $$\hat{\beta}_{is}^{min,ref} = \hat{\beta}^{ref}_{is(k)} - 1.96 SD_{is},\quad \hat{\beta}_{is}^{max,ref} = \hat{\beta}^{ref}_{is(k)} + 1.96 SD_{is}$$

        \item  Our method provides estimates of the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We compute the accuracy of the $\beta$ estimation through a bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of trade costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 confidence interval for each couple $i,s$. Writing $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the size of the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the referee's method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

@@

    \item We can then evaluate the accuracy of each estimation method by comparing the size of the confidence intervals of the $\beta$, for each couple $i,s$ (by year and transport mode). We summarize this comparison in Figure \ref{fig:accuracy_beta}, which reports the distribution of the ratio of confidence intervals, taken in log.

    \begin{figure}[htbp]
    \caption{Accuracy of the estimation of the $\beta$: Comparison}
    \label{fig:accuracy_beta}
    \begin{center}
    \includegraphics[height=3in]{../../revised_article/comparaison_amplitude_baseline_referee1_2013_ves.png}
    \begin{minipage} [c]  {5in} \scriptsize%
    	    Note: Ratio of the confidence intervals = $ _{}ln(CI_{is}/CI^{ref}_{is})$
    \end{minipage}

    \end{center}
    \end{figure}

   \textbf{XXXX AJouter le complement sur Air et stop XXX} In most cases, the log of the ratio is negative, implying a smaller interval confidence of the baseline $\beta$ estimation. Our method thus yields more accurate estimations of the share of additive components, whatever the transport mode considered. We have checked that a similar conclusion applies on other years (they are not reported here for sake of brevity but they are available upon request).
    \end{itemize}

One explanation of the limited accuracy of the direct method might be the following. Given that the estimation method is run at the country-sector level (exploiting heterogeneity \textit{within} a given country-sector pair), it implicitly assumes that transport costs are independent \textit{across} sectors and \textit{across} origin countries. In plain words, it assumes that transport costs of say, cars, have nothing in common whether those goods comes from France or from Germany; or that transport costs that apply to imported goods from France have no common component across sectors. This is a disputable assumption. From a statistical point of view, it implies leaving aside information contained in the fact that transport costs have a both a country-specific component and a sector-specific component. We believe that explains the better accuracy of the baseline estimation.

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

%The two stories are not necessarily incompatible, however.

%Nevertheless, the point made by the referee is an important one and deserves careful investigation. We devoted a lot of thought to a potential switch from weight to quantity.
%Running the estimation considering quantities (i.e., units) rather than weight, still on the transport mode-yearly basis yet appears really uneasy in our context for several, non-trivial reasons, that we develop below.

\subsubsection{Data availability issue}

The first difficulty is availability of information on quantities. Neither the US Bureau of Census data nor the 1974-2004 Hummels's data (based on the Census Bureau data) report the quantity by transport mode. This is incompatible with our empirical strategy of estimation which is conditional on the transport mode, similarly as in \cite{hummels2007}. As a result, computing the unit price of all trade flows would require the assumption that the weight per unit is the same for vessel shipments and air shipments at the level of the observation. This is unlikely, as one would expect the higher value-to-weight varieties to be transported by air rather than by vessel. The alternative is to consider only single-mode flows. In Hummels's data (1974-2014), on average 41.1 \% of trade flows and 79\% of trade value are multi-mode. This would reduce the total value of the sample from 12,500 billion dollars to 2,650 billion dollars, entailing a large loss of useful information. Original census data, when accessible, are more promising.\footnote{Original Census data are  reported at the HS-10 digit $\times$ district of entry $\times$ district of unleading $\times$ rate provision code.} In 2019, multi-modal flows are 570 billion dollars out of 1,790 billion dollars, or 31\% of the data. This is still a large share, but not too large to preclude any work. Accordingly, we dig deeper into this issue with the US Census dataset, restricted to single transport mode flows. \smallskip

@@

Quantity units are a second difficult. The Census data remain silent on that matter. To the best of our knowledge, these can only be found in the ``Harmonized Tariff Schedule of the United State''. Unfortunately, these schedules change many time per year and only the schedules from 2009 onwards are available in a .csv format on the Census website. On the years for which the match could be done (from 2009), it turns out that at our sector level (3-digit), goods (either at the 5-digit or the 10-digit level) are measured in different units. In 2019, only 125 3-digit sectors out of 230 are measured in a single unit (after cleaning up the unit names\footnote{As units are not always coherent (eg weight can be given in ``kg’’, ``kg.'' ``Kg'' and, also, ``g'' and ``t'').}).\footnote{For instance, 3-digit SITC sector ``061 Sugar, molasses and honey'' includes among other products, 5-digit SITC product ``6150 Molasses, whether or not decolourized'', measured in liters and 5-digit SITC product ``06160 Natural Honey'' measured in kg. Actually worse than this, the 5-digit SITC product ``06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel'' includes both 10-digit HTS product ``1702903500 Other: invert molasses'', measured in liters and 10-digit HTS product ``1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions''  measured in kg.} Neglecting these differences would invalidate our functional forms, as no one expects the transport cost of a ``piece'' to be the same as the transport cost of a ``kg'', even in the same sector.
So we are limited to using quantity units from 2009 to 2019, amending our structure of fixed effects to consider the triplet (origin country, sector, quantity unit).

\subsubsection{Estimation issue}

Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight prices. As discussed above, in our baseline regression we separate each transport cost component in two distinct sector-country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could be easily replaced by (sector, quantity unit) fixed effects; but the same does not appear relevant for country fixed effects. Let us elaborate on this issue.

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

Quantity units are a second difficult. The Census data remain silent on that matter. To the best of our knowledge, these can only be found in the ``Harmonized Tariff Schedule of the United State''. Unfortunately, these schedules change many time per year and only the schedules from 2009 onwards are available in a .csv format on the Census website. On the years for which the match could be done (from 2009), it turns out that at our sector level (3-digit), goods (either at the 5-digit or the 10-digit level) are measured in different units. In 2019, only 125 3-digit sectors out of 230 are measured in a single unit (after cleaning up the unit names\footnote{As units are not always coherent (eg weight can be given in ``kg’’, ``kg.'' ``Kg'' and, also, ``g'' and ``t'').}).\footnote{For instance, 3-digit SITC sector ``061 Sugar, molasses and honey'' includes among other products, 5-digit SITC product ``6150 Molasses, whether or not decolourized'', measured in liters and 5-digit SITC product ``06160 Natural Honey'' measured in kg. Actually worse than this, the 5-digit SITC product ``06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel'' includes both 10-digit HTS product ``1702903500 Other: invert molasses'', measured in liters and 10-digit HTS product ``1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions''  measured in kg.} Neglecting these differences would invalidate our functional forms, as no one expects the transport cost of a ``piece'' to be the same as the transport cost of a ``kg'', even in the same sector.
So we are limited to using quantity units from 2009 to 2019, amending our structure of fixed effects to consider the triplet (origin country, sector, quantity unit).

\subsubsection{Estimation issue}

Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight prices. As discussed above, in our baseline regression we separate each transport cost component in two distinct sector-country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could be easily replaced by (sector, quantity unit) fixed effects; but the same does not appear possible for country fixed effects. Let us elaborate on this issue.

@@

In the per-weight price, the existence of a single country fixed effect applicable to all sectors is justified, as a kilogram is always a kilogram and one can assume they both add the same to transport costs from, say, Germany. In contrast, an unit of tee-shirt is quite different from an unit of car. To clarify this point, consider imports of tee-shirts and cars from
Germany and China. Under the separability assumption, importing a tee-shirt from either country implies paying the cost given by the  country fixed effect (the same for all sectors) plus the cost given by
the sector fixed effect ; and similarly for importing a car.
Hence, the difference in the cost of importing a car from Germany versus China would be the same, in dollars, as the difference between the cost of importing a tee- shirt from Germany relative to China. This does not seem a sensible assumption.
In this setting, we cannot keep the separability assumption.
As discussed before, this dramatically increases the computational difficulty of our method (with no substantial different results, see Subsection 3.3.1. in the main paper).\smallskip

Integrating these various constraints, we run the robustness check (weight versus quantity) \textit{i)} on a sample reduced over 2009-2019, considering single transport mode flows - amounting to 66\% of the value of the baseline sample; \textit{ii)} retaining a non-separable structure of three-dimensional fixed effects $t_{is(k)u}$, $\tau_{is(k)u}$ according to the following equation:
\begin{equation*}
\ln\left(\frac{p_{iku}}{\widetilde{p}_{iku}}-1 \right)= \ln \left(\tau_{is(k)u} -1+\frac{t_{is(k)u} }{\widetilde{p}_{iku}} \right) + \epsilon_{iku}
\end{equation*}
\noindent where $p_{iku}$ refers to the cif price associated with quantity of goof $k$ imported from country $i$, measured in unit $u$ (eg kg or number), $\widetilde{p}_{iku}$ the corresponding unit value (fas price).

@@

\begin{table}[htbp]
	\caption{Comparison: Price per quantity versus per kg, 2009-2019}
	\begin{center}		
		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy_reshaped.tex}
%		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy.tex}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
			\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
		\end{tabular}
	\end{center}
		\label{graph_comp_wgt_qty}%
\end{figure}

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions that strongly limit both the number of sectors and of countries covered, do also impact the value of trade flows covered. In our view, this raises a non-trivial sample selection bias that reduces the general scope of the transport cost estimates. Second, in terms of $\beta$ estimates, the results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air). In this regard, they stand in line with the results of \cite{Lashkaripour_JIE2020}, and confirm the correlation between weight per unit and unit price. Still, the share of additive cost is not reduced to zero (except if one looks at the median for vessel). Thus these results do not disqualify our approach, especially as we cover a much larger period and sample with our baseline estimate.

\subsubsection{On the relevance of the per-weight price approach}
At a more fundamental level, we do believe that the study of transport costs measured on a per-weight price add some relevant information on the international transport cost burden faced by exporters. Let us explain why.
